### 2025-02-20 analysis/analysis.qmd

### By genre + feature complexity

```{r}
# m.cor_complexity <- update(m.cor.c, 
#        subgroup = C_summary$feature_n_complexity_genre, 
#        tau.common = FALSE,
#        prediction = TRUE)
# 
# print(m.cor_complexity)
```
### By model type

>>>>

### By feature complexity

```{r}
m.cor_complexity <- update(m.cor.c,
       subgroup = C_summary$feature_n_complexity,
       tau.common = FALSE,
       prediction = TRUE)

print(m.cor_complexity)

```
### By model type
